Harnessing the skill estimation using Bayesian Inference: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2020-12-18 article.tex
paper TTT: detalles en la intro

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{Harnessing Skill estimation using Bayesian Inference: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages}
\Plaintitle{Harnessing Skill estimation using Bayesian Inference: the Julia, Python and R packages}
%\title{All the concepts behind TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages}
%\Plaintitle{All the concepts behind TrueSkill Through Time: the Julia, Python and R packages}
\Shorttitle{TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages (Draft)}

@@

\en{Elo's methodological solution is simple and smart: update both previous estimates, $s_{i_\text{old}}$ and $s_{j_\text{old}}$, based on the surprise (i.e. the complement of the prediction of the observed result).}
\es{La soluci\'on metodol\'ogica de Elo es simple y astuta: actualizar las estimaciones previas, $s_{i_\text{old}}$ y $s_{j_\text{old}}$, en base a la sorpresa (i.e. el complemento de la predicci\'on del resultado observado).}
%
\begin{equation} \label{eq:elo_delta}
 \Delta = \underbrace{\left(1-P(\,r\,|\,s_{i_\text{old}},s_{j_\text{old}}\,)\right)}_{\text{\en{Surprise}\es{Sorpresa}}}
\end{equation}
%
\en{where the probability arises from instantiating the previous estimates, $s_{i_\text{old}}$ and $s_{j_\text{old}}$, in the generative model (details in section~\ref{sec:exactSolution}).}
\es{Donde la probabilidad surge de instanciar las estimaciones previas en el modelo generativo (detalles en la sección~\ref{sec:exactSolution}).}
%
\en{The idea is that the surprise $\Delta$ depends on how accurate are the previous estimates and, therefore, can be used to update them.}
\es{La idea es que la sorpresa $\Delta$ depende de cuan buenas son las estimaciones previas y por lo tanto sirve para actualizarlas.}
%
\en{Unexpected results would indicate that current estimates should be updated to a greater extent than if they had occurred as expected.}
\es{Los resultados inesperados indicar\'ian que las estimaciones actuales no son del todo correctas y deber\'ian actualizarse en mayor medida que si hubieran ocurrido como se esperaba.}
%
\begin{equation}\label{eq:elo_update}
 s_{\text{winner}_\text{new}} = s_{\text{winner}_\text{old}} + \Delta \ \ \ \ \ s_{\text{loser}_\text{new}} = s_{\text{loser}_\text{old}} - \Delta 
\end{equation}
%
\en{where the surprise $\Delta$ acts as a correction factor for both previous estimates.}
\es{Donde la sopresa $\Delta$ act\'ua como factor de correcci\'on para ambas estimaciones previas.}
%
\en{This procedure can recover the relative scale of the agents, starting from arbitrary initial values.}
\es{Esta soluci\'on puede recuperar la escala relativa de los agentes, partiendo de de valores iniciales arbitrarios.}
%
\en{However, it does have a major weaknesses.}
\es{Sin embargo, tiene algunas debilidades importantes.}
%
\en{The update rule (Eq.~\ref{eq:elo_update}) is symmetric, so what one agent wins is lost by the other.}
\es{La regla de actualizaci\'on (Eq.~\ref{eq:elo_update}) es sim\'etrica, as\'i que lo que un agente gana el otro lo pierde.}
%
\en{Because new agents start with arbitrary estimates (the same initial value is used for all individuals), they tend to generate high surprise and abruptly modify estimates that had already converged.}
\es{Debido a que a los agentes nuevos comienzan con estimaciones arbitrarias (el mismo valor inicial para cualquier individuo), ellas tienden a generan alta sorpresa y a modificar bruscamente estimaciones que ya hab\'ian convergido.}
%
\en{The weak point is due to the lack of the notion of uncertainty.}
\es{El punto débil se debe a la falta de la noción de incertidumbre.}
%
\en{To solve this problem, an ad-hoc solution was proposed: reducing the impact of the surprise based on the number of times the agent has participated previously.}
\es{Para resolver este problema, una soluci\'on ad-hoc fue propuesta: reducir el impacto de la sorpresa en funci\'on de la cantidad de veces que el agente ha participado previamente.}
%
% \en{This is the role played by the K-factor used by FIDE,  $\Delta_i = \Delta \cdot K_i$.}
% \es{Ese es rol que desempe\~na el K-factor usado por la FIDE, $\Delta_i = \Delta \cdot K_i$.}

@@

\en{A superior solution, instead of selecting a single value as an estimate, involves quantifying the ``relative certainty'' associated with each of the skill hypotheses.}

@@

\en{All inference, no matter how complex it is, can be solved by the rules of probability: the~\ref{eq:sum_rule} and the~\ref{eq:product_rule}.}

@@

\en{The \ref{eq:sum_rule} states that any marginal distribution can be obtained by integrating, or summing up, the joint distribution:}

>>>>

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{Harnessing the skill estimation using Bayesian Inference: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages}
\Plaintitle{Harnessing the skill estimation using Bayesian Inference: the Julia, Python and R packages}
\Shorttitle{TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages (Draft)}

@@

\en{Elo's methodological solution is simple and smart: update both previous estimates, $s_{i_\text{old}}$ and $s_{j_\text{old}}$, based on the surprise (i.e. the complement of the prediction of the observed result).}
\es{La soluci\'on metodol\'ogica de Elo es simple y astuta: actualizar las estimaciones previas, $s_{i_\text{old}}$ y $s_{j_\text{old}}$, en base a la sorpresa (i.e. el complemento de la predicci\'on del resultado observado).}
%
\begin{equation} \label{eq:elo_delta}
 \Delta = \underbrace{\left(1-P(\,r\,|\,s_{i_\text{old}},s_{j_\text{old}}\,)\right)}_{\text{\en{Surprise}\es{Sorpresa}}}
\end{equation}
%
\en{where the probability arises from instantiating the previous estimates, $s_{i_\text{old}}$ and $s_{j_\text{old}}$, in the generative model (details in section~\ref{sec:exactSolution}).}
\es{Donde la probabilidad surge de instanciar las estimaciones previas en el modelo generativo (detalles en la sección~\ref{sec:exactSolution}).}
%
\en{The idea is that the surprise $\Delta$ depends on how accurate are the previous estimates and, therefore, can be used to update them.}
\es{La idea es que la sorpresa $\Delta$ depende de cuan buenas son las estimaciones previas y por lo tanto sirve para actualizarlas.}
%
\en{Unexpected results would indicate that current estimates should be updated to a greater extent than if they had occurred as expected.}
\es{Los resultados inesperados indicar\'ian que las estimaciones actuales no son del todo correctas y deber\'ian actualizarse en mayor medida que si hubieran ocurrido como se esperaba.}
%
\begin{equation}\label{eq:elo_update}
 s_{\text{winner}_\text{new}} = s_{\text{winner}_\text{old}} + \Delta \ \ \ \ \ s_{\text{loser}_\text{new}} = s_{\text{loser}_\text{old}} - \Delta 
\end{equation}
%
\en{where the surprise $\Delta$ acts as a correction factor for both previous estimates.}
\es{Donde la sopresa $\Delta$ act\'ua como factor de correcci\'on para ambas estimaciones previas.}
%
\en{This procedure can recover the relative scale of the agents, starting from arbitrary initial values.}
\es{Esta soluci\'on puede recuperar la escala relativa de los agentes, partiendo de de valores iniciales arbitrarios.}
%
\en{However, it does have a major weaknesses.}
\es{Sin embargo, tiene algunas debilidades importantes.}
%
\en{The update rule (Eq.~\ref{eq:elo_update}) is symmetric: what one agent wins is lost by the other.}
\es{La regla de actualizaci\'on (Eq.~\ref{eq:elo_update}) es sim\'etrica, as\'i que lo que un agente gana el otro lo pierde.}
%
\en{Because new agents start with arbitrary estimates (the same initial value is used for all individuals), they tend to generate greater surprise values and abruptly modify estimates that had already converged.}
\es{Debido a que a los agentes nuevos comienzan con estimaciones arbitrarias (el mismo valor inicial para cualquier individuo), ellas tienden a generan alta sorpresa y a modificar bruscamente estimaciones que ya hab\'ian convergido.}
%
\en{The weak point is to not have into account the notion of uncertainty.}
\es{El punto débil se debe a la falta de la noción de incertidumbre.}
%
\en{To solve this problem, an ad-hoc solution was proposed: reducing the impact of the surprise based on the number of times the agent has participated previously.}
\es{Para resolver este problema, una soluci\'on ad-hoc fue propuesta: reducir el impacto de la sorpresa en funci\'on de la cantidad de veces que el agente ha participado previamente.}
%
% \en{This is the role played by the K-factor used by FIDE,  $\Delta_i = \Delta \cdot K_i$.}
% \es{Ese es rol que desempe\~na el K-factor usado por la FIDE, $\Delta_i = \Delta \cdot K_i$.}

@@

\en{An improved alternative consists in quantifying the uncertainty associated with each of the skill hypotheses instead of selecting a single value.}

@@

\en{All inference, independently of its complexity, can be solved by the rules of probability: the~\ref{eq:sum_rule} and the~\ref{eq:product_rule}.}

@@

\en{The \ref{eq:sum_rule} states that any marginal distribution can be obtained by integrating, or summing up, the joint probability:}
